Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-05 paper.tex
improved overview figure

The Helmholtz machine~\cite{dayan1995helmholtz} introduced the idea of alternating between
learning a generative model and training a recognition model on samples from the generative model.
We apply this same idea to the problem of program induction,
and so we call our algorithm the \system.
Figure~\ref{feeding} diagrams how these three steps feed off of each other.
\begin{figure}\centering
  \begin{tikzpicture}
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](DSL) at (6,4) {DSL: $\mathcal{D}$};
    \node[align = center](synthesis) at (4,2) {Search for \\programs: $p$};
    \node[ align = center](recognitionModel) at (6,0) {Recognition \\model: $q$};

    \draw [->,thick] (DSL.west) to[out = 180,in = 90] node[above,rotate = 45]{{\footnotesize Makes tractable}} (synthesis.north);
    \draw [->,thick] (synthesis.east) to[out = 0,in = -90] node[above,rotate = 70]{{\footnotesize Trains}} (DSL.south);
    \draw [->,thick] (synthesis.east) to[out = 0,in = 90] node[below,rotate = -60]{{\footnotesize Trains}} (recognitionModel.north);
    \draw [->,thick] (recognitionModel.west) to[out = 180,in = -90] node[below,rotate = -70]{{\footnotesize Makes tractable}} (synthesis.south);
    \draw [->,thick] (DSL.east) to[out = 0,in = 0] node[above,rotate = -90]{{\footnotesize Trains}} (recognitionModel.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm alternatingly solves for the programs, DSL, and recognition model. Each of these steps bootstraps off of the others.}  \label{feeding}
  \end{figure}

>>>>

The Helmholtz machine~\cite{dayan1995helmholtz} introduced the idea of alternating between
learning a generative model and training a recognition model on samples from the generative model.
We apply this same idea to the problem of program induction,
and so we call our algorithm the \system.
Figure~\ref{feeding} diagrams how these three steps feed off of each other.
\begin{figure}\centering
  \begin{tikzpicture}
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $q$};

    \draw [->,thick] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45]{{\footnotesize Trains}} (DSL.30);
    \draw [->,thick] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45]{{\footnotesize Trains}} (recognitionModel.150);
    \draw [->,thick] (DSL.east) to[out = -30,in = 210] node[above]{{\footnotesize Trains}} (recognitionModel.west);

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others.}  \label{feeding}
  \end{figure}
